Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-04-23 krs-survey.tex
Reorganizing the conclusion, started to affine content

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary of Approaches}
\label{sect|summary}

@@

This section tries to summary the various approaches we surveyed in the
previous section.  This summary does not exactly follow the list of compared
features presented in section~\ref{sect|features}. We have organized
it along four axis: \emph{what can be represented?}, \emph{How knowledge is
created and grounded?}, \emph{What can be done with the knowledge?} and
\emph{How to use knowledge in the whole, larger robot architecture?}.

@@

\begin{itemize}
	\item expressiveness
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Towards the next generation of Knowledge Representation Systems for Robotics}
\label{sect|conclusion}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Towards the next generation of Knowledge Representation Systems for Robotics}
\label{sect|conclusion}

This section tries to summary the various approaches we surveyed in the
previous sections and to draw some research perspectives. This section does not
exactly follow the list of compared features presented in
section~\ref{sect|features}. We have organized it along four axis: \emph{what
can be represented?}, \emph{How knowledge is created and grounded?}, \emph{What
can be done with the knowledge?} and \emph{How to use knowledge in the whole,
larger robot architecture?}.

Table~\ref{table|contribution-by-systems} proposes a summary of the main scopes
of \emph{contribution} of the systems we have surveyed. This overview helps to
identify the main weaknesses of current approaches of knowledge representation
regarding the long-term goal of \emph{human-level robots}.

@@

@@

\begin{itemize}
    \item common-sense knowledge
    \begin{itemize}
        \item \emph{default reasoning}
        \item \emph{uncertainty representation/reasoning}
        \item \emph{physics-based reasoning}
    \end{itemize}
    \item Spatio-temporal representations
    \item Meta-cognition and introspection
    \item Context
\end{itemize}

@@
